An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-08 poly-embed-journal/poly-embed-journal.tex
Post meeting updates to Theorem 12 and Prop 10

	It remains to show (iii).
  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg. 455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
  Therefore, we must have $H^+ \in \H$ as well.
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
%	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
%	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
%	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
%	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H$. 
%	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

%  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
\end{proof}

@@

Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
\begin{claim}\label{claim:gV-equals-riskL}
	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_{L(\R)})
	&\iff g_{L(\R)}(x) \geq c & \text{definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$}\\
    &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$, minimizability} \\
    % as the infimum % over $v \in {L(\R)}$ of}\\
    % & & \text{the inner product with $x$ and minimizable;} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{definition of $H^+_v$}\\
	&\iff (x,c) \in \cap \H_{L(\R)} & 
	\end{align*}
	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. \jessiet{Omitting details on why $\V \subseteq {L(\R)}$.}
	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
\end{proof}

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  Then
  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  (ii) $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.\raft{Is $F_v$ defined?  Looks like it got cut (we were going to move it to this subsec maybe)}
  (iii) $\V^* \subseteq \V$.
  (iv) $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
  (iv)   The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
  Thus $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
\end{proof}

@@

Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
If $P$ is understood from context, we simply denote this face $F_v$.
We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.

@@

%Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	Given $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_{\V^*})}_v = H_v \cap \hyp(g_{\V^*})$.
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*})$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $d-1 = |\Y| = \dim(F_v) = \dim(\pi(F_v))$.
\end{proof}

@@

\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $\V' \subseteq L(\R)$, we have
	$\cup_{v\in\V'} \pi(F^{\hyp(g_{\V^*})}_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	\jessiet{Revisit- just rewrote (Mar 10)}
	For any $v \in \V$, define $F_v := F^{\hyp(g_{\V^*})}_v$.
	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption. %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

We now claim that a set of projected faces $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ \jessiet{Diff between $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ and $\{F^{\hyp(g_{\V^*})}_v\}_{v \in \V'}$?}for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{L(\R)})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.

\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
	Let $F_v := F^{\hyp(g_{L(\R)})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
	%For $\V' \subseteq \V$, 
	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda_{\V^*}  \subseteq \Lambda_{\V'}$.
	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
	$\implies$
	The result follows if $\V^* \subseteq \V'$, which follows from the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda_{\V^*} \cap \Lambda_{\V'} = \Lambda_{\V^*}$.
	%$\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

@@

\btw{Lemmatta for Lemma showing (7) in Lemma \ref{lem:X}}
\begin{claim}\label{claim:vface-subset-some-vstar-face}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For any $v \in L(\R)$, the face $F^{\hyp(g_{\V^*})}_{v} \subseteq F^{\hyp(g_{\V^*})}_{v^*}$ for some $v^* \in \V^*$. \jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{proof}
	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though. Old version in comments}
	As $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.

>>>>

	It remains to show (iii).
	Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
	It suffices to show that, (a) for each facet $F$ of $P$, there is an $H^+ \in \H$ such that $F = H\cap P$, and (b) if $F$ is a facet of $P$ and $H,H'$ are hyperplanes with $F = H \cap P = H' \cap P$, then it must be the case that $H = H'$.
	For (a), \citet[Proposition 3.17]{gallier2008notes} observes that, for all $x \in \partial P$, there exists some hyperplane $\hat H$ such that $\hat H$ supports $P$ at $x$.
	Moreover, the hyperplanes defining facets are unique, as noted in the last sentence of the proof of \citep[Proposition 4.5]{gallier2008notes}.
	Since $x \in \relint(F)$ is in exactly one face of $F$, namely $F$ itself, there must be a unique $H^+ \in \H$ such that $F = H \cap P$.
	For (b), consider that if $F$ is a facet of $P$, which is $d$-dimensional, its affine hull is a hyperplane in $\reals^d$.
	As hyperplanes are uniquely defined, it must be the case that $H = H'$.
%  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
%  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
%  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg. 455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
%  Therefore, we must have $H^+ \in \H$ as well.

@@

Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
\begin{claim}\label{claim:gV-equals-riskL}
	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_{L(\R)})
	&\iff g_{L(\R)}(x) \geq c & \text{definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$}\\
    &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$, minimizability} \\
    % as the infimum % over $v \in {L(\R)}$ of}\\
    % & & \text{the inner product with $x$ and minimizable;} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{definition of $H^+_v$}\\
	&\iff (x,c) \in \cap \H_{L(\R)} & 
	\end{align*}
	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. 
	Now, to construct a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, iterate over each of the (finitely many) faces of $g_{L(\R)}$.
	For each face $F^{(i)}$ consider $x^{(i)} \in \relint(F^{(i)})$.
	There is some $v^{(i)} \in L(\R)$ such that $H_{v^{(i)}}$ supports $\hyp(g_{L(\R)})$ at $x^{(i)}$~\citep[Proposition 3.17]{gallier2008notes}.
	Then $\V = \{v^{(i)}\}_i \subseteq L(\R)$ and is finite by construction.
	To show that $g_{L(\R)} = g_\V$, we equivalently show their hypographs are equal.
	Let $\H_\V := \{H^+_{v}\}_{v \in \V}$.
	Observe that we can write $\hyp(g_{L(\R)}) = \cap (\H_{L(\R)} \cup \H_\Y)$, and $\hyp(g_\V) = \cap(\H_\V \cup \H_\Y)$.
	Since each $H^+_{v^{(i)}}$ is a valid halfspace for $\hyp(g_{L(\R)})$, we immediately have $\hyp(g_{L(\R)}) \subseteq \hyp(g_{\V})$.
	To observe the reverse inequality, consider that $\V$ was constructed via the faces of $\hyp(g_{L(\R)})$, which includes the facets.
	As $x^{(i)}$ on the relative interior of a facet must be defined by a unique supporting hyperplane $v^{(i)}$, we have the set $\H_\V$ must be a superset of the set of hyperplanes defining the facets of $\hyp(g_{L(\R)})$.
	Therefore, $g_{\V} \subseteq g_{L(\R)}$, and thus the two are equal.
	\jessiet{Added construction on how to get all the faces.}
	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
\end{proof}

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  Then
  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  (ii) $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.\raft{Is $F_v$ defined?  Looks like it got cut (we were going to move it to this subsec maybe) define in line}
  (iii) $\V^* \subseteq \V$.
  (iv) $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
  (iv)   The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
  Thus $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
\end{proof}

@@

When the set $\V^*$ is clear, we denote the faces of $\hyp(g_{\V^*})$ by $F_v := H_v \cap \hyp(g_{\V^*})$.
We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.

@@

%Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*})$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $d-1 = |\Y| = \dim(F_v) = \dim(\pi(F_v))$.
\end{proof}

@@

\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $\V' \subseteq L(\R)$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	\jessiet{Revisit- just rewrote (Mar 10)}
	%For any $v \in \V$, define $F_v := F^{\hyp(g_{\V^*})}_v$.
	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption. %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

We now claim that a set of projected faces $\{F_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F_v) \mid v \in S\}$ as the set of projected facets generated by $S$.

\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
	%Let $F_v := F^{\hyp(g_{L(\R)})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
	%For $\V' \subseteq \V$, 
	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda_{\V^*}  \subseteq \Lambda_{\V'}$.
	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
	$\implies$
	The result follows if $\V^* \subseteq \V'$, which follows from the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda_{\V^*} \cap \Lambda_{\V'} = \Lambda_{\V^*}$.
	%$\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

@@

\btw{Lemmatta for Lemma showing (7) in Lemma \ref{lem:X}}
\begin{claim}\label{claim:vface-subset-some-vstar-face}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For any $v \in L(\R)$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. \jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{proof}
	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though. Old version in comments}
	As $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
